---
title: "AssignmentWeek2DevelopmentDataProduct"
---
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(leaflet))
```

This file was created by Sandro on the following date:

```{r date, comment=""}
date()
```

## Download precipitation data 
Data were obtained from the R dataset of Annual Precipitation in US Cities.  
The average amount of precipitation (rainfall) in inches for each of 70 United States (and Puerto Rico) cities.   
Source: Statistical Abstracts of the United States, 1975
References: McNeil, D. R. (1977) Interactive Data Analysis. New York: Wiley.
```{r, precipitation R dataset}

data("precip")
cities.precip<-as.factor(names(precip))
values<-as.data.frame(precip)
df.precip<-cbind.data.frame(cities.precip, values)
```

## Download coordinates data 
US cities geographic coordinates were obtained from the website www.gaslampmedia.com
```{r,coordinates data}

url<-"https://www.gaslampmedia.com/wp-content/uploads/2013/08/zip_codes_states.csv"

download.file(url, destfile = "coordinates.csv", method = "curl")
coordinates<-read.csv("coordinates.csv")
cities<-select(coordinates, "latitude", "longitude", "city", "state")

cities<-(cities)%>%group_by(city)%>%mutate(lat=median(latitude), lng=median(longitude))%>%select(city, lat, lng)%>%unique()
    

```

## Matching data
```{r,matching df}

geo<-merge.data.frame(cities, df.precip, by.x = "city", by.y = "cities.precip")
```

##Plot of US cities precipitations
```{r, warning=FALSE, message=FALSE, fig.align='center',fig.cap='US cities precipitations'}
geo %>%
   leaflet() %>%
   addTiles() %>%
   addCircles(weight = 1, radius = geo$precip * 1000, popup=geo$city)
```
